moderated_regressions

### 2024-05-10 moderated_regressions.Rmd
updating regression tables. yet need to align numbers and add plot of the interaction

#r squared
cr_burn_m2_r <- round(summary(cr_burn_m2)$r.squared,2)
cr_burn_m3_r <- round(summary(cr_burn_m3)$r.squared,2)

## R square change
cr_burn_anova <- anova(cr_burn_m2, cr_burn_m3)
cr_burn_r_square_change <- round(cr_burn_m3_r - cr_burn_m2_r,2)

@@

#r squared
cr_stress_m2_r <- round(summary(cr_stress_m2)$r.squared,2)
cr_stress_m3_r <- round(summary(cr_stress_m3)$r.squared,2)

## R square change
cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
cr_stress_r_square_change <- round(cr_stress_m3_r - cr_stress_m2_r,2)

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(chal.2.eng, res.2.eng, int.cr.3.eng, chal.2.stress, res.2.stress, int.cr.3.stress, chal.2.burn, res.2.burn, int.cr.3.burn)
R <- c("", cr_eng_m2_r, cr_eng_m3_r, "", cr_stress_m2_r, cr_stress_m3_r, "", cr_burn_m2_r, cr_burn_m3_r)
DeltaR <- c("","",cr_eng_r_square_change, "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)

regtable <- cbind(DV, Step, Model, Beta, R, DeltaR)
papaja::apa_table(regtable)
```

@@

papaja::apa_table(regtable,
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01")
# How to get delta symbol and superscript
#https://cran.r-project.org/web/packages/reporter/vignettes/reporter-super.html#:~:text=To%20get%20superscripts%20or%20subscripts,to%20the%20desired%20cell%20value.

>>>>

#r squared
cr_burn_m2_r <- summary(cr_burn_m2)$r.squared
cr_burn_m3_r <- summary(cr_burn_m3)$r.squared

## R square change
cr_burn_anova <- anova(cr_burn_m2, cr_burn_m3)
cr_burn_r_square_change <- sigfill(cr_burn_m3_r - cr_burn_m2_r)

@@

#r squared
cr_stress_m2_r <- summary(cr_stress_m2)$r.squared
cr_stress_m3_r <- summary(cr_stress_m3)$r.squared

## R square change
cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
cr_stress_r_square_change <- sigfill(cr_stress_m3_r - cr_stress_m2_r)

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(chal.2.eng, paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)

#paste(round(hr_eng_m3_r,2),"**")

regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))

papaja::apa_table(regtable,
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01")

#https://stackoverflow.com/questions/67088456/r-aligning-table-content-to-decimal-points-in-kable

#tribble(
#  ~Variable_1,~Variable_2,
#  "13.5","4.4**",
#  "12.7***","1.2*",
#  "0.4","0.3***",
#  "2.3**","11.5**"
#)%>%
#  rename_all( ~ str_c("{ ",.," }"))%>%
#  kable(format = "latex", booktabs=T, escape = T)%>%
#  kable_styling(position = "center", latex_options = "hold_position")
```

@@

papaja::apa_table(regtable,
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01")
```
